When Cities Change Hands: Extinctions of Dynasties and \\Breaks in the Development of N German Cities

### 2023-02-16 paper/paper.tex
add abstract and initial writeups

This is like \cite{as1997} and \cite{aw1998} and also \cite{as1997} and also \cite{olken2005}. hi there \cite{olken2005}

>>>>

I estimate the effect of state size on development using a panel of construction events in cities of the Holy Roman Empire. I exploit variation from lineage extinctions, which caused cities to become part of different lineages' territorial holdings. I find that X. I discuss economic mechanisms that explain this effect.
